Analyzing X-ray images in Python with scikit-image

### 2016-08-21 skimage_tomo.tex
Add Jupyter example screenshot and caption

The Jupyter notebook \citep{Kluyver2016} is a web application that grew
out of the IPython project. Jupyter notebooks provide an interactive development
environment within a web browser, where live code can be enriched
by explanatory text, equations and visualizations (FIGURE).
As of July 2016, more than 500,000 Jupyter notebooks were posted on GitHub,
demonstrating their wide adoption by the community as workflow-sharing
tools (\url{http://archive.ipython.org/media/SciPy2016JupyterLab.pdf}).

>>>>

The Jupyter notebook \citep{Kluyver2016} is a web application that grew
out of the IPython project. Jupyter notebooks provide an interactive development
environment within a web browser, where live code can be enriched
by explanatory text, equations and visualizations (Fig.~\ref{fig:jupyter}).
As of July 2016, more than 500,000 Jupyter notebooks were posted on GitHub,
demonstrating their wide adoption by the community as workflow-sharing
tools (\url{http://archive.ipython.org/media/SciPy2016JupyterLab.pdf}).

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{jupyter_example}}
    \caption{\csentence{The Jupyter notebook} allows mixing of computer code (top),
             plot and text output (middle), and free-form narrative text (bottom).
             This makes it ideal to record and report code-based analyses.
             Screenshot from \url{https://gist.github.com/jni/3339985a016572f178d3c2f18e27ec0d}.
 \label{fig:jupyter}}
\end{figure*}
